---
title: "Modern M&A - Custom Xaringan Theme"
subtitle: "⚔<br/>with xaringan"
author: "The Authors Names ... just meta-data"
date: "2019/08/16 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    seal: false
    css: [theme/src/css/kunoichi.css,       theme/src/css/ninjutsu.css,
          theme/src/css/ninpo.css,          theme/src/css/default.css,
          theme/src/css/default-fonts.css,  theme/src/css/custom-fonts.css,
          theme/usr/css/custom.css,         assets/css/deck.css]
    chakra: theme/src/js/remark.min.js
    lib_dir: libs
    nature:
      ratio: 16:10
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      navigation:
        scroll: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(fig.path = "assets/img/")
library(anicon)
```

```{asis notes, include=FALSE}
# NOTES:

```

```{r child="slides/theme.Rmd"}
```

---
```{r child="slides/1-title.Rmd"}
```

---
```{r child="slides/2-preface.Rmd"}
```

---
```{r child="slides/3-setup.Rmd"}
```

---
```{r child="slides/4-git-and-friends.Rmd"}
```

---
```{r child="slides/5-ssh-keys.Rmd"}
```

---
```{r child="slides/6-ssh-config.Rmd"}
```

---
```{r child="slides/7-git-config.Rmd"}
```

---
class: split-10 m1 nopadding-h2

.row.center[
# 2 Methods -  Getting Started
]

.row.split-two[.column[.content[
## Brand New Repo
#### Adding a local git config
```bash
git config user.name "First Last"
git config user.email ""
```
#### Adding a remote repository
```bash
git remote add origin git@esgovcloud.com:mAndA/clone-me.git
```
]]
.column[.content[
## Preexisting Repo
#### Cloning
]]]

---
name: resources
class: nomargin-ul nomargin-h2 nomargin-h4 nopadding-h2

## <center>Presentation Resources</center>

.pull-left[
#### Friends of Git
Windows
- [Git for Windows](https://gitforwindows.org)
- [Terminal Emulator](https://esgovcloud.com/mAndA/savi/blob/master/CONTRIBUTING.md#windows-10)
- [chocolatey](https://chocolatey.org), [scoop](https://scoop.sh), [winget](https://github.com/microsoft/winget-cli)

macOS
- [Homebrew](https://brew.sh)
- [iTerm2](https://www.iterm2.com/index.html)

#### SSH Keys
- [Connecting to GitHub with SSH](https://docs.github.com/en/github/authenticating-to-github/connecting-to-github-with-ssh)
- [GitLab and SSH keys](https://docs.gitlab.com/ee/ssh/README.html)
- [Demo Repo to Clone](https://esgovcloud.com/mAndA/clone-me)
]

.pull-right[

]
